Correcting for bias in high throughput sequencing data

### 2011-06-16 seqbias-paper.tex
new data and plots

@@

\begin{table}
\processtable{
    The $R^2$ goodness of fit statistic measures increased uniformity in read
    coverage, after correcting for bias. Here the median $R^2$ across the test
    exons is listed for each method and simple. A positive $R^2$ indicates a
    better fit.\label{tab:pois}}{
    \begin{tabular}{lcccc}\toprule
          & BN    & MART  & GLM   & 7mer \\\midrule
Wetterbom & 0.168 & 0.016 & 0.066 & -0.079 \\
Katze     & 0.283 & 0.243 & 0.158 & 0.033 \\
Bullard   & 0.271 & 0.163 & 0.224 & 0.157 \\
Mortazavi & 0.225 & 0.210 & 0.197 & 0.091 \\
Trapnell  & 0.298 & 0.289 & 0.248 & 0.138
    \end{tabular}
}{}
\end{table}

>>>>

Our own method was trained on the 200,000 reads from chromosomes 1--8, with the
highest number of duplicates.

@@

\begin{table}
\processtable{
    The $R^2$ goodness of fit statistic measures increased uniformity in read
    coverage, after correcting for bias. Here the median $R^2$ across the test
    exons is listed for each method and simple. A positive $R^2$ indicates a
    better fit.\label{tab:pois}}{
    \begin{tabular}{lcccc}\toprule
          & BN    & MART  & GLM   & 7mer \\\midrule
Wetterbom & 0.173 & 0.016 & 0.066 & -0.079 \\
Katze     & 0.286 & 0.243 & 0.158 & 0.033 \\
Bullard   & 0.276 & 0.163 & 0.224 & 0.157 \\
Mortazavi & 0.248 & 0.210 & 0.197 & 0.091 \\
Trapnell  & 0.308 & 0.289 & 0.248 & 0.138
    \end{tabular}
}{}
\end{table}
